data_collation

### 2024-05-23 scripts/data_collation.Rmd
updaated site info with master

# Combine site.info dataframes
```{r}

# site information data is cleaned and ready

# Make all columns capitalized
colnames(Site_info_2018) <- toupper(colnames(Site_info_2018))

# combine site collection data
site.info.dat <- rbind.fill(Site_info_2017, Site_info_2018, Site_info_template_v1)

# remove columns with observer and unneeded data
site.info.dat <- site.info.dat[ -c(12:15) ]

@@

# Austin - the site info for 2018 has a start and stop latitude so don't know what to do here

>>>>

# Combine site.info dataframes
```{r}
#site info cleaned metadta
# combine site collection data
site.info.dat <- kelp_siteinfo_MASTER

@@
